### 2021-09-03 manuscript/tables.tex
Tabelas 2,3 e 4 com as medias e desvios padroes dos residuos testes sinteticos e reais

>>>>

\tabl{mean_std}{This table shows the means and standard deviations for each residual presented in the synthetic data tests between the observation data in comparison to the classical solution and our solution.
\label{tab:mean_std}}
{
	\begin{center}
		\begin{tabular}[]{|l|c|c|}
			\hline
			Residual                                                      & Mean   & Std \\
			\hline 
			Noiseless grid classical solution                             & 0.3627 & 0.2724 \\
			\hline
			Noiseless grid our solution                                   & 0.5223 & 0.4323 \\
			\hline
			X, Y - 20\% noise grid classical solution                     & 0.3630 & 0.2731 \\
			\hline
			X, Y - 20\% noise grid our solution                           & 0.7147 & 0.5622 \\
			\hline
			X, Y - 30\% noise grid classical solution                     & 0.3634 & 0.2735 \\
			\hline
			X, Y - 30\% noise grid our solution                           & 0.9788 & 0.7462 \\
			\hline
			Z - 05\% noise surface classical solution                     & 0.3712 & 0.2870 \\
			\hline
			Z - 05\% noise surface our solution                           & 0.9542 & 0.8943 \\
			\hline
			Z - 10\% noise surface classical solution                     & 0.3865 & 0.3216 \\
			\hline
			Z - 10\% noise surface our solution                           & 1.6109 & 1.6231 \\
			\hline
		\end{tabular}
	\end{center} 
}

\tabl{mean_std_upward}{This table shows the means and standard deviations for each residual presented in the synthetic data tests section for the upward continuation transformation comparison.
	\label{tab:mean_std_upward}}
{
	\begin{center}
		\begin{tabular}[]{|l|c|c|}
			\hline
			Residual                                                      & Mean   & Std \\
			\hline
			Noiseless grid upward continuation classical solution         & 0.5130 & 0.6533 \\
			\hline
			Noiseless grid upward continuation our solution               & 0.6127 & 0.8121 \\
			\hline
			Noiseless grid upward continuation Fourier solution           & 2.1120 & 2.2870 \\
			\hline
			X, Y - 20\% noise grid upward continuation classical solution & 0.5060 & 0.6427 \\
			\hline
			X, Y - 20\% noise grid upward continuation our solution       & 0.6764 & 0.8147 \\
			\hline
			X, Y - 20\% noise grid upward continuation Fourier solution   & 2.1025 & 2.2774 \\
			\hline
			X, Y - 30\% noise grid upward continuation classical solution & 0.4988 & 0.6324 \\
			\hline
			X, Y - 30\% noise grid upward continuation our solution       & 0.7477 & 0.7796 \\
			\hline
			X, Y - 30\% noise grid upward continuation Fourier solution   & 2.1116 & 2.2763 \\
			\hline
			Z - 05\% noise surface upward continuation classical solution & 0.4979 & 0.6380 \\
			\hline
			Z - 05\% noise surface upward continuation our solution       & 1.5656 & 0.9857 \\
			\hline
			Z - 05\% noise surface upward continuation Fourier solution   & 2.0925 & 2.2907 \\
			\hline
			Z - 10\% noise surface upward continuation classical solution & 0.4792 & 0.6234 \\
			\hline
			Z - 10\% noise surface upward continuation our solution       & 4.2127 & 2.3897 \\
			\hline
			Z - 10\% noise surface upward continuation Fourier solution   & 2.0728 & 2.2924 \\
			\hline
		\end{tabular}
	\end{center} 
}

\tabl{mean_std_real_data}{This table shows the means and standard deviations for the residuals presented in the real data tests section, for the solution of the regular interpolated grid and the irregular decimated grid.
	\label{tab:mean_std_real_data}}
{
	\begin{center}
		\begin{tabular}[]{|l|c|c|}
			\hline
			Residual                               & Mean   & Std \\
			\hline
			Regular interpolated grid              & 0.0735 & 0.3172 \\
			\hline
			Irregular decimated grid               & 0.0798 & 0.5060 \\
			\hline
		\end{tabular}
	\end{center} 
}
